Phenotypes_Planting_2019

### 2020-01-06 data-raw/phenotypes_2019.Rmd
Modify phenotypes_2019 and metadata to have AP13 values

source("C:/Users/alice/Documents/Github/Functions_ggplot-theme-adjustments_2018-01-03.R")
theme_set(theme_poster)

@@

```{r}
wb_pheno <- loadWorkbook(file.path("C:", "Users", "alice", "Dropbox",
                                   paste0("GWAS DOE Switchgrass, ",
                                          "Consolidated Data"),
                                   paste0("DOE_GWAS_2019_Consolidated ",
                                          "Pheno Data_12-25-19.xlsx")))
lst_pheno <- readWorksheet(wb_pheno, sheet = getSheets(wb_pheno))
phenos_planting1 <- lst_pheno$`GWAS 2019 Greenup Data`
phenos_planting2 <- lst_pheno$`GWAS 2019 Core Phenotype Data`
phenos_key <- lst_pheno$`Column Key and Notes`

wb_KING2019 <- loadWorkbook(file.path("C:", "Users", "alice", "Dropbox",
                                      paste0("GWAS DOE Switchgrass, ",
                                             "Consolidated Data"),
                                      "Individual Site Files",
                                      "KING_GWAS_2019_Chlorosis Data.xlsx"))
lst_KING2019 <- readWorksheet(wb_KING2019, sheet = getSheets(wb_KING2019))
KING2019 <- as_tibble(lst_KING2019$`KING GWAS 2019 Chlorosis`)
key_KING19 <- as_tibble(lst_KING2019$`COLUMN KEY`)

wb_DEAD2018 <- loadWorkbook(file.path("C:", "Users", "alice", "Dropbox",
                                      paste0("GWAS DOE Switchgrass, ",
                                             "Consolidated Data"),
                                      "Forms and Miscellaneous",
                                      paste0("GWAS_2019_Mortality, Weak and ",
                                             "Not P. Virgatum Plants_ARCHIVE.xlsx")))
lst_DEAD2018 <- readWorksheet(wb_DEAD2018, sheet = getSheets(wb_DEAD2018))
DEAD2018 <- as_tibble(lst_DEAD2018$`GWAS 2019 Dead Only`)
LOST2018 <- as_tibble(lst_DEAD2018$`GWAS 2019 Dead, Weak, Not PV`)

@@

metadata <- add_row(metadata, PLANT_ID = "AP13", LIB_CLIMATE = "Y", LIB_PHENO = "Y", LIB_ACC = "Y", Ecotype = "TX", Genetic_subpop = "TX")
```

>>>>

source("../../../Github/Functions_ggplot-theme-adjustments_2018-01-03.R")
theme_set(theme_poster)

@@

```{r}
wb_pheno <- loadWorkbook(file.path("C:", "Users", "ahm543", "Dropbox",
                                   paste0("GWAS DOE Switchgrass, ",
                                          "Consolidated Data"),
                                   paste0("DOE_GWAS_2019_Consolidated ",
                                          "Pheno Data_12-25-19.xlsx")))
lst_pheno <- readWorksheet(wb_pheno, sheet = getSheets(wb_pheno))
phenos_planting1 <- lst_pheno$`GWAS 2019 Greenup Data`
phenos_planting2 <- lst_pheno$`GWAS 2019 Core Phenotype Data`
phenos_key <- lst_pheno$`Column Key and Notes`

wb_KING2019 <- loadWorkbook(file.path("C:", "Users", "ahm543", "Dropbox",
                                      paste0("GWAS DOE Switchgrass, ",
                                             "Consolidated Data"),
                                      "Individual Site Files",
                                      "KING_GWAS_2019_Chlorosis Data.xlsx"))
lst_KING2019 <- readWorksheet(wb_KING2019, sheet = getSheets(wb_KING2019))
KING2019 <- as_tibble(lst_KING2019$`KING GWAS 2019 Chlorosis`)
key_KING19 <- as_tibble(lst_KING2019$`COLUMN KEY`)

wb_DEAD2018 <- loadWorkbook(file.path("C:", "Users", "ahm543", "Dropbox",
                                      paste0("GWAS DOE Switchgrass, ",
                                             "Consolidated Data"),
                                      "Forms and Miscellaneous",
                                      paste0("GWAS_2019_Mortality, Weak and ",
                                             "Not P. Virgatum Plants_ARCHIVE.xlsx")))
lst_DEAD2018 <- readWorksheet(wb_DEAD2018, sheet = getSheets(wb_DEAD2018))
DEAD2018 <- as_tibble(lst_DEAD2018$`GWAS 2019 Dead Only`)
LOST2018 <- as_tibble(lst_DEAD2018$`GWAS 2019 Dead, Weak, Not PV`)

@@

# metadata <- metadata %>%
#   filter(PLANT_ID != "AP13")

metadata <- add_row(metadata, PLANT_ID = "AP13", LIBRARY = "REF", LIB_CLIMATE = "Y", LIB_PHENO = "Y", LIB_ACC = "Y", JL_genetic_subpop = "TX", JL_detail_genetic = "TX", PLOIDY = "4X", Ecotype = "TX", Genetic_subpop = "TX")

save(metadata, file = "../data/metadata.rda")
```
